\section{Questionnaires}\label{app:quest}
\def\ctick{$\onontimes$}
\def\myscale#1#2{%
    &\space\expandafter\myscaleA\expandafter{\the\numexpr#1\expandafter}%
    \expandafter{\the\numexpr#2}% evaluate params
}
\def\myscaleA#1#2{#1\space&\ifnum#1<#2 \space \myscaleB{\the\numexpr#1+1\relax}{#2}\fi}
\def\myscaleB#1\fi{\fi \expandafter\myscaleA\expandafter#1}

\def\ticks#1#2#3#4{%
    #1&\space\expandafter\ticksA\expandafter{\the\numexpr#2\expandafter}%
    \expandafter{\the\numexpr#3}#4% evaluate params
}
\def\ticksA#1#2{\ctick\space&\ifnum#1<#2 \space \ticksB{\the\numexpr#1+1\relax}{#2}\fi}
\def\ticksB#1\fi{\fi \expandafter\ticksA\expandafter#1}


\newcommand\linearSacle[3]%
  {\newcount\cols%
   \cols=#1%
   \advance\cols by 2%
  \begin{tabular}{*{\cols}{c}}
     \myscale{1}{#1} \\
     \ticks{#2}{1}{#1}{#3} \\
  \end{tabular}%
}

\newcommand\YesNo{%
    \begin{tabular}{cl} 
        \ctick & Yes \\
        \ctick & No \\
    \end{tabular}
}

\subsection{Questionnaire A}
Pre-experiment Self Assessment

\begin{enumerate}
    \item In a scale from 1 to 5, how would you describe your UML knowledge?
        \linearSacle{5}{Novice}{Expert}
    \item Have you ever created a UML Profile in the past? \\
        \YesNo
    \item In a scale from 1 to 5, how would you describe your Papyrus Tool expertise? \\
        \linearSacle{5}{Novice}{Expert}
    \item Have you ever created a UML Profile using Papyrus in the past? \\
        \YesNo
\end{enumerate}

\subsection{Questionnaire B}
Post-experiment Self Assessment
\begin{enumerate}
    \item Overall, do you feel the time assigned to the tasks was enough? \\
        \YesNo
    \item On a scale of 1 to 10, how easy it was to find the documentation needed to perform the tasks? \\
        \linearSacle{10}{Very Hard}{Very Easy}    
\end{enumerate}

For each task:
\begin{enumerate}
    \item On a scale of 1 to 10, before the essential information was given, how confident did you feel about completing this task? \\
        \linearSacle{10}{Very Hard}{Very Easy}
    \item On a scale of 1 to 10, after the essential information was given, how confident did you feel about completing this task? \\
        \linearSacle{10}{Very Hard}{Very Easy}
    \item Did you found the given time to complete the task sufficient? \\
        \YesNo
    \item Did you, at any point before receiving the essential information, felt completely lost on how to complete the task? \\
        \YesNo
    \item If you answered yes to the previous question, is this because:\\
        \begin{tabular}{cp{0.8\textwidth}} 
            \ctick & The task objective was not clear to me \\
            \ctick & I didn’t know how to complete the task although it was clear to me what I the goal is \\
            \ctick & Other...(Please provide details below)
        \end{tabular}\\
        Other: \underline{\hspace{0.9\textwidth}}
    \item On a scale from 1 to 10, how much easier was the task to complete after receiving the essential information?\\
     \linearSacle{10}{No difference}{Much easier}
\end{enumerate}


